---
title: "Lab 00 - Hello IDS!"
author: "Felix Ainsley"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Katya Cheltsova", "Aimee Tumblety", "Kayleigh Innes", 
           "Freddie Elson", "Felix Ainsley"),
  github_username = c("katya/c", "aimeet05", "kayleighinnes", 
                      "freddodercfish", "fjohna"), 
  colour = c("purple1", "blue", "green", 
             "orange", "purple"),
  hobby = c("piano", "Guitar", "Movies", 
            "Gym", "Table Tennis"),
  favourite_number = c(4, 7, 69, 4, 13)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


a graph of favourite numbers based on github username through data in the table

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github username", 
          y = "favourite number",
          title = "groups favourite numbers")
```



### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

a table due to extreme variation in results, which would allow for a more tidy presentation
